Concrete Semantics for Pushdown Analysis:\\The Essence of Summarization

### 2013-10-03 content.tex
Added example that CPS isn't as precise and tested in the redex model.

%%
This paper gives a common, simple framework to derive both CFA2 and PDCFA using a recipe to apply pushdown analysis techniques to arbitrary semantics in a manner similar to AAM.
%
To exercise the recipe further, we give a novel analysis for delimited, composable control. \\

@@

%% TODO: complete
\paragraph{Comparison to CFA2 CPS'd to remove {\tt shift} and {\tt reset}:}{
  One might ask what this different model buys us over using a CPS transform to compile away {\tt shift} and {\tt reset} forms.
%
The short answer is that we get better precision for capture and invocation of continuations.
%
In pushdown analysis, we track function return points with entire calling contexts rather than the $k$-CFA way of allocating the continuation in the heap at some lower-precision address, like a variable.
%
In our summarizing analysis of delimited composable control, we get the same added precision for {\tt reset}, {\tt shift}, and continuation invocation points.
%
Consider the following program and its CPS transform for comparison:
\begin{lstlisting}
???
\end{lstlisting}

\begin{lstlisting}
???
\end{lstlisting}

PDCFA with a monovariant allocation strategy will predict the CPS'd version returns ???.
%
Our specialized analysis for delimited control, also with a monovariant allocation strategy, will predict the non-CPS'd version returns ???.}

>>>>

%%
This paper gives a common, simple framework to derive CFA2, PDCFA and its garbage-collecting extension using a recipe to apply pushdown analysis techniques to arbitrary semantics in a manner similar to AAM.
%
To exercise the recipe further, we give a novel analysis for delimited, composable control. \\

@@

%% TODO: complete
\paragraph{Comparison to PDCFA CPS'd to remove {\tt shift} and {\tt reset}:}{
  One might ask what this different model buys us over using a CPS transform to compile away {\tt shift} and {\tt reset} forms.
%
The short answer is that we get better precision for capture and invocation of continuations.
%
In pushdown analysis, we track function return points with entire calling contexts rather than the $k$-CFA way of allocating the continuation in the heap at some lower-precision address, like a variable.
%
In our summarizing analysis of delimited composable control, we get the same added precision for {\tt reset}, {\tt shift}, and continuation invocation points.
%
Consider the following program and its CPS transform for comparison:
\begin{lstlisting}[mathescape]
(let* ([id ($\lambda$ (x) x)]
       [f ($\lambda$ (y) (shift k (k (k y))))]
       [g ($\lambda$ (z) (reset (id (f z))))])
  (<= (g 0) (g 1)))
\end{lstlisting}

\begin{lstlisting}[mathescape]
(let* ([id ($\lambda$ (x k) (k x))]
       [f ($\lambda$ (y j) (j (j y)))]
       [g ($\lambda$ (z h) (h (f z ($\lambda$ (fv) (id fv ($\lambda$ (i) i))))))])
  (g 0 ($\lambda$ (g0v) (g 1 ($\lambda$ (g1v) (<= g0v g1v))))))
\end{lstlisting}

PDCFA with a monovariant allocation strategy will predict the CPS'd version returns true or false.
%
Our specialized analysis for delimited control, also with a monovariant allocation strategy, will predict the non-CPS'd version returns true.}
